---
title: "Geometric Brownian Motion"
output: html_notebook
---

These notes follow the code provided in [Kirs Longmore's tutorial](https://robotwealth.com/efficiently-simulating-geometric-brownian-motion-in-r/).

## Libraries
```{r libraries, message=FALSE}
library(tidyverse)
```


## General Formula
Geometric Brownian motion is a stochastic differential equation of the form:

$$
S(t) = S_0\left(\left(\mu - \frac{\sigma^2}{2}\right)t + \sigma B_t\right) 
$$

where $S_0$ is the initial value, $\mu$ is the drift coefficient, $\sigma$ is the volatility coefficient, $t$ is the current time period, and $B_t$ is the Brownian motion and $B_t \sim N(0,t)$ for all $t$.

## Simulation Model

```{r sim-model}
gbm_vec <- function(nsim, S0, t, mu, sigma, dt = 1./365){
  B <- matrix(rnorm(t*nsim), ncol = nsim, nrow = t)
  
  # get GBM and convert to price paths
  gbm <- exp((mu - sigma * sigma / 2) * dt + sigma * B * sqrt(dt))
  gbm <- apply(rbind(rep(S0, nsim), gbm), 2, cumprod)
  
  return(gbm)
}

nsim <- 50
t <- 100
mu <- 0
sigma <- 0.1
S0 <- 100

gbm <- gbm_vec(nsim, S0, t, mu, sigma)
colnames(gbm) <- paste("Sim_", 1:nsim)

gbm_df <- gbm %>%
  as_tibble() %>%
  mutate(index = 1:nrow(gbm)) %>%
  pivot_longer(-index, names_to = 'sim', values_to = 'price')

gbm_df %>%
  ggplot(aes(x = index, y = price, color = sim)) +
  geom_line() +
  theme(legend.position = 'none')
```

## Price Distribution
```{r price-distribution}
nsim <- 20000
t <- 100
mu <- 0
sigma <- 0.1
S0 <- 100

gbm <- gbm_vec(nsim, S0, t, mu, sigma)
price_df <- tibble(price = gbm[t, ]) #last price
price_df %>%
  ggplot(aes(x = price)) +
  geom_histogram(aes(y=..density..), binwidth = 0.1) +
  geom_density()

```

From here we can use this distribution in a Monte Carlo simulation.